% ME4370 - Mechatronics - Tristan Hill
% Guest Lecture - March 2, 0216

% Timing - MCUs and PCs - Deterministic vs. Non Deterministic 

% Document settings
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{color,soul}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}

\pagestyle{plain}
\setlength\parindent{0pt}
\hypersetup{
bookmarks=true,         % show bookmarks bar?
unicode=false,          % non-Latin characters in Acrobat’s bookmarks
pdftoolbar=true,        % show Acrobat’s toolbar?
pdfmenubar=true,        % show Acrobat’s menu?
pdffitwindow=false,     % window fit to page when opened
pdfstartview={FitH},    % fits the width of the page to the window
pdftitle={My title},    % title
pdfauthor={Author},     % author
pdfsubject={Subject},   % subject of the document
pdfcreator={Creator},   % creator of the document
pdfproducer={Producer}, % producer of the document
pdfkeywords={keyword1} {key2} {key3}, % list of keywords
pdfnewwindow=true,      % links in new window
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with linkbordercolor)
citecolor=green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=blue           % color of external links
}


\newcommand{\HSIZ}{3mm}
\newcommand{\VSIZ}{3mm}

\begin{document}
    
	\textbf{\LARGE ME 4370 - Mechatronics - Spring 2016}\\\\
	\textbf{\LARGE {\it It is all about it Timing - PCs vs. MCUs}}\\
	    \begin{description}
        \item[\textbf{Overview}]\textbf{:}\\\\
        
            A microcontroller, or MCU is fundamentally different from a personal computer. MCUs are capable of operating on {\it precise} timing rountines while personal computers run on a {\it non-deterministic} timing. Therefore, one specialized capability of an MCU is precise timing of input and output as well as internal events. Personal computers cannot do this. 
        
        \item[\textbf{Measure Time}]\textbf{:}\\    
            
            How could we make a timer? Lets talk about some ideas. 
                \begin{enumerate}
                    \item moon and stars (sun)
                    \item seasons
                    \item sand, hourglass
                    \item pendulum, time based on $\omega_n$ 
                \end{enumerate}
            
            We use CRYSTALS !!! 
            
        \item[\textbf{Timing on a PC}]\textbf{:}\\  
            Why does it take so long for a to PC application to load? What is going on in the background that we are not seeing? The short answer is, very many things all at once. 
        
    \end{description}
\end{document}



